---
title: "6. extra leaflet functionality"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: yes
    theme: united
vignette: >
  %\VignetteIndexEntry{6. extra leaflet functionality}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 8.83, message = FALSE, warning = FALSE)
```

Package **leafem** provides a few extra `add*` functions for use with leaflet (and mapview).

- `addMouseCoordinates` - add a box with mouse position, projection information and zoom level information
- `addLogo` - add images to maps
- `addHomeButton` - add zoom-to button to a map
- `addFeatures` - add features to a map, regardless of features type unresposnive

Here are some examples:

## addMouseCoordinates

let's us add mouse position information along with detailed information about the layer's projection and zoom level information. By default, only `lon`, `lat` and `zoom` are shown. To also show info on the `epsg code` and the `proj4string` press and hold Ctrl and move the mouse. `addMouseCoordinates` also allows us to copy the info about the current mouse position to the clipboard by holding the Ctrl and left-clicking on the map.

```{r addmc default}
library(mapview)
library(leaflet)
library(leafem)

leaflet() %>% addTiles() %>% leafem::addMouseCoordinates()
```

------

## addLogo

can be used to add logos (or any type of image really) to a map

```{r logo r}
library(leafem)
img <- "https://www.r-project.org/logo/Rlogo.svg"
leaflet() %>% addTiles() %>% leafem::addLogo(img, url = "https://www.r-project.org/logo/")
```

<br>

arguments `offset.x`, `offset.y` together with `position` give control about image placement. See `?addLogo` for details

```{r logo banana}
m <- mapview(breweries)
library(leafem)

leafem::addLogo(m, "https://jeroenooms.github.io/images/banana.gif",
                position = "bottomleft",
                offset.x = 5,
                offset.y = 40,
                width = 100,
                height = 100)
```

------

## addHomeButton

can be used to add 'zoom-to-layer' buttons to a map. By default located in the bottom-right corner of the map (can be changed using argument `position`)

```{r home}
library(raster)
library(leafem)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(data = breweries91) %>% 
  leafem::addHomeButton(ext = extent(breweries91), group = "Breweries")
```

------

## addFeatures

is a type agnostic `add*` function which will call the approprate `leaflet::add*` function based on the provided feature type (points, lines, polygons). It is currently defined for handling objects from packages `sf` and `sp`. For `sf` objects, in addition to the standard feature types `POINT`, `MULTIPOINT`, `LINESTRING`, `MULTILINESTRING`, `POLYGON` and `MULTIPOLYGON` it can also handle features of type `sfc_GEOMETRY` which are a collection of mixed types.

```{r addpols}
library(leafem)

leaflet() %>% addTiles() %>% leafem::addFeatures(breweries)
```

<br>

The standard styling arguments for `leaflet::add*` functions can be used just like in the original `add*` function

```{r addpols style}
library(leafem)

leaflet() %>% 
  addTiles() %>% 
  leafem::addFeatures(franconia, weight = 1, fillColor = "grey", color = "black",
              opacity = 1, fillOpacity = 0.6)
```

<br>
