---
title: "7. ceci constitue la fin du pipe"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: yes
    theme: united
vignette: >
  %\VignetteIndexEntry{7. ceci constitue la fin du pipe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 8.83, message = FALSE, warning = FALSE)
```

**mapview** can be used in piped expressions using `%>%`, most likely at the very end of it...

Here are just a few examples of piped workflows:

## `plot`ting feature unions

```{r pipe1a}
library(mapview)
library(leaflet)
library(dplyr)
library(sf)
library(albersusa)

franconia %>%
  st_union %>%
  plot
```

<br>

## `mapview`ing feature unions

```{r pipe1b}
franconia %>%
  st_union %>%
  mapview
```

<br>

## union by district

```{r pipe2}
franconia %>%
  group_by(district) %>%
  summarize %>%
  mapview(zcol = "district")
```

<br>

## districts by area

```{r pipe3}
franconia %>%
  group_by(district) %>%
  summarize %>%
  mutate(area = st_area(.) / 1e6) %>%
  mapview(zcol = "area")
```

<br>

## counties by area

```{r pipe4}
franconia %>%
  mutate(area = sf::st_area(.)) %>%
  mapview(zcol = "area", legend = TRUE)
```

<br>

## breweries colored by district

```{r pipe5}
breweries %>%
  st_intersection(franconia) %>%
  mapview(zcol = "district")
```

<br>

## number of breweries by county

```{r pipe6}
franconia %>%
  mutate(count = lengths(st_contains(., breweries))) %>%
  mapview(zcol = "count")
```

<br>

## brewery density by county

```{r pipe7}
franconia %>%
  mutate(count = lengths(st_contains(., breweries)),
         density = count / st_area(.)) %>%
  mapview(zcol = "density")
```

<br>

## using `native.crs` for a USA composite map

```{r pipe8a}
albersusa::usa_composite("laea") %>%
  mapview(native.crs = TRUE, zcol = "pop_2014", legend = TRUE)
```

<br>

## without `native.crs`

```{r pipe8b}
albersusa::usa_composite("laea") %>%
  mapview(zcol = "pop_2014", legend = TRUE)
```

