---
title: "5. extra functionality"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: yes
    theme: united
vignette: >
  %\VignetteIndexEntry{5. extra functionality}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 8.83, message = FALSE)
library(mapview)
```

**mapview** provides a couple of special convenience functions for all supported spatial data types:

- `viewExtent` to view extents/bounding boxes of objects
- `sync`ing of multiple maps

There are also a few *raster-only* specialty functions:

- `viewRGB` to view RGB (raster) images

For the following:

- `plainview` to view raster images without map background
- `slideview` to compare two raster/RGB images
- `cubeview` to view 3D raster cubes

please refer to the individual help pages (e.g. `?cubeview`)

# All types

## viewExtent

This can be handy to check whether features overlap or to just check where things are roughly located (e.g. in case we have big data sets, e.g. raster stacks).

```{r extent1}
viewExtent(poppendorf, color = "red") + viewExtent(breweries)
```

------

## sync & latticeView

`sync` can be used to produce small multiples that are synchronised. Meaning that if we zoom into one panel, all other panels will also zoom. Additionally, the mouse position is also synced (indicated via a red circle). `sync` provides a very convenient way to compare multiple attributes of the same feature geometry set.

We can `sync` all panels:

```{r sync all}
m1 <- mapview(breweries, zcol = "village", map.types = "Esri.WorldImagery")
m2 <- mapview(breweries, zcol = "brewery", col.regions = heat.colors)
m3 <- mapview(breweries, zcol = "founded", legend = TRUE)
m4 <- leaflet() %>% addTiles() %>% addCircleMarkers(data = breweries)

sync(m1, m2, m3, m4)
```

<br>

Any combination of panels:

```{r sync selected}
sync(list(m1, m2, m3, m4),
     sync = list(c(1, 4),
                 c(2, 3)))
```

<br>

We can also control the layout by specifying how many columns we want to have (rows will be automatically set):

```{r sync col}
sync(list(m1, m2, m3), ncol = 1)
```

<br>

`latticeView` will render small multiples without synchronising

```{r lattice}
latticeView(m1, m3)
```

<br>

------

# Raster-only

## viewRGB

`viewRB` can be used to view true- or false-color raster images. It expects a `RasterStack` or `RasterBrick` and the default setting will render layer combination 3-2-1

```{r true rgb}
viewRGB(poppendorf, r = 4, g = 3, b = 2)
```

<br>

```{r false rgb}
viewRGB(poppendorf, 5, 4, 3)
```
