---
title: "4. mapview popups"
output:
  rmarkdown::html_document:
    toc: true
    theme: united
vignette: >
  %\VignetteIndexEntry{4. mapview popups}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(fig.width = 8.83, mesage = FALSE)
library(mapview)
```
------

**mapview** provides a few special popup rendering functions. These can be used to generate:

1. attribute table popups
2a. graph popups (i.e. plots in popups)
2b. interactive popups
3. image popups

## Attribute table popups

`popupTable` is the standard popup function used in mapview. It provides a static table rendering of all attributes of the individual features.

```{r popupTable}
mapview(breweries, popup = popupTable(breweries,
                                      zcol = c("brewery",
                                               "village",
                                               "founded")))
```

<br> 

This can also be used with leaflet maps 

```{r popupTable leaflet}
leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = breweries,
                   popup = popupTable(breweries))
```

------

## Graph popups

`popupGraph` allows us to include static or interactive (htmlwidgets) plots in popups. In the following example we will show a scatterplot of copper ~ cadmium for each individual feature of the famous meuse data set

```{r popupGraph meuse}
library(lattice)
library(sp)

data(meuse)
coordinates(meuse) <- ~x+y
proj4string(meuse) <- CRS("+init=epsg:28992")

p <- xyplot(copper ~ cadmium, data = meuse@data, col = "grey", pch = 20, cex = 2)
p <- mget(rep("p", length(meuse)))

clr <- rep("grey", length(meuse))
p <- lapply(1:length(p), function(i) {
  clr[i] <- "red"
  update(p[[i]], col = clr)
})


mapview(meuse,
        zcol = "cadmium",
        popup = popupGraph(p))
```

------

## Interactive popups

Here's a rather silly example of an interactive popup. I am sure there's many more sensible examples but for the fun of it here's a map in a map popup. 

**A WARNING:** Including interactie popups can quickly lead to very large files that will take a long time to render and also become rather unresponsove.

```{r popupGraph interactve}
brew1 <- breweries91[1, ]

mapview(brew1,
        popup =  popupGraph(mapview(brew1,
                                    map.types = "Esri.WorldImagery")@map,
                            type = "html"))
```

------

## Image popups

`popupImage` can be used to include images in popups. Both local (file) and remote (web url) images can be used.

```{r popup image url}
library(sf)
pnt <- data.frame(x = 174.764474, y = -36.877245)
pnt <- st_as_sf(pnt, coords = c("x", "y"), crs = 4326)

img <- "https://upload.wikimedia.org/wikipedia/commons/thumb/6/62/Mount_Eden.jpg/640px-Mount_Eden.jpg"

mapview(pnt, map.types = "Esri.WorldImagery",
        popup = popupImage(img, src = "remote"))
```

<br>

**IMPORTANT NOTICE** for those who want to save maps locally (see chapter `mapview save maps` for details): With the current implementation of `popupImage` (local only) and `popupGraph` we need to save the popup files (graphs, images) in a folder called `popup_graphs` which needs to be located one level above the map widget. Hence, when saving a map locally (with `mapshot` or `saveWisget`) we need to manually copy that folder to on elevel above the destination folder where the map is saved. This should soon be solved but for the time being, in case you don't see any popup images or graphs in your locally saved map, make sure to copy the appropriate folder (which is usually generated in your computers `temp` directory). 
